---
title: "Homework-3-Tidyverse"
format: pdf
editor: visual
---

## Task 1
### Question a

We cannot directly use the read_csv() function because data.txt is delimited by semicolons and not commas. Instead, we can use read_csv2().

```{r}
#| warning: false
library(tidyverse)
library(palmerpenguins)

data <- read_csv2("C:/Users/ZRose/Desktop/Skewl/ST_558/Homework3/data/data.txt")
data
```

### Question b
```{r}
data2 <- read_delim("C:/Users/ZRose/Desktop/Skewl/ST_558/Homework3/data/data2.txt",
                    delim = "6", col_types = "fdc")
data2
```

## Task 2
### Question a
```{r}
#| warning: false
trailblazer <- read_csv(
  "C:/Users/ZRose/Desktop/Skewl/ST_558/Homework3/data/trailblazer.csv"
)
glimpse(trailblazer)
```

### Question b
```{r}
trailblazer_longer <- trailblazer |>
  pivot_longer(
    cols = starts_with("Game"),
    names_to = "GameLabel",
    values_to = "Points"
  ) |>
  separate_wider_delim(
    cols = GameLabel,
    delim = "_",
    names = c("Game", "Location")
  )

head(trailblazer_longer, 5)
```

### Question c
```{r}
trailblazer_longer |>
  pivot_wider(
    names_from = Location,
    values_from = Points
  ) |>
  group_by(Player) |>
  summarise(
    mean_home = mean(Home, na.rm = TRUE),
    mean_away = mean(Away, na.rm = TRUE),
    diff_home_away = mean_home - mean_away
  ) |>
  arrange(desc(diff_home_away))
```
On average, Jusuf Nurkic, Robert Covington, Nassir Little, Damian Lillard, and
Cody Zeller scored more points at home through the first 10 games of the season
than away.

## Task 3
### Question a
Species and island aren't unique identifiers for each row.  This is because there can
be multiple penguins of the same species on each island.  Some entries are $<\mbox{NULL}>$
because there aren't any values for that combination of species and island.  Some
values are like $<\mbox{dbl [52]}>$ because there are many values for that combination
of species and island (52 of them).  The way these combinations are selected results in
a list of doubles.  We see that the columns are $<\mbox{list}>$ as they contain a list
of bill length values rather than a single value.

### Question b
```{r}
penguins |>
  group_by(species, island) |>
  summarise(n = as.double(n())) |>
  pivot_wider(names_from = island, values_from = n, values_fill = 0)
```

## Task 4
```{r}
penguins |>
  mutate(bill_length_mm = case_when(
    is.na(bill_length_mm) & species == "Adelie" ~ 26,
    is.na(bill_length_mm) & species == "Gentoo" ~ 30,
    TRUE ~ bill_length_mm
  )) |>
  arrange(bill_length_mm) |>
  slice_head(n = 10)
```